Stats for the convergence paper

### 2019-12-17 models/paper/convergence_paper_models.Rmd
confint table

@@

```{r }
test2$lex_typicality = factor(test2$lex_typicality, levels = c('typical', 'random', 'atypical'))
test2$reg_rate = factor(test2$reg_rate, levels = c('nc', '-40%', '+40%'))
test2$baseline_av_z = scales::rescale(test2$baseline_av)
test2$pre_reg_av_z = scales::rescale(test2$pre_reg_av)
test2$baseline_av_c = test2$baseline_av - mean(test2$baseline_av)
test2$pre_reg_av_c = test2$pre_reg_av - mean(test2$pre_reg_av)

fit1 = brm(resp_post_reg ~ 1 + baseline_av_z * lex_typicality + pre_reg_av_z + reg_rate +
    (1 | participant_id) + 
    (1 | word), 
  data = test2, 
  family = bernoulli, 
  control=list(adapt_delta=0.99, stepsize = 0.01, max_treedepth =15))

@@

```{r }
# the frequentist fit reported in the paper
# watch out for factor levels
# lex typ: typical - random - reversed
# reg rate: nc - -40% - +40%
test2$lexical_typicality = test2$lex_typicality
test2$regularisation_rate = ifelse(
  as.character(test2$reg_rate) == 'nc', 'no change',
  as.character(test2$reg_rate)
  )
test2$regularisation_rate = factor(test2$regularisation_rate, levels = c('no change', '-40%', '+40%'))

lme.fit2 = glmer(resp_post_reg ~ 1 + baseline_av_c * lexical_typicality + pre_reg_av_c + regularisation_rate +
    (1 + baseline_av_c | participant_id) + 
    (1  | word), 
  data = test2, 
  family = binomial (link = logit),
  control=glmerControl(optimizer="bobyqa")
)
summary(lme.fit2)$coef

plot(effects::effect('regularisation_rate', lme.fit2), main = '', xlab = 'regularisation shift', ylab = 'regular response in post-test')
plot(effects::effect('baseline_av_c:lexical_typicality', lme.fit2), multiline = T, lines=list(lty=c(1,2,3)), main = '', xlab = 'verb baseline mean', ylab = 'regular response in post-test')

@@

Let's have a few estimates for CI-s.

@@

confint(lme.fit2, method = 'Wald', level = 0.95)
effects::allEffects(lme.fit2)

>>>>

# moving factors round
test2$lex_typicality = factor(test2$lex_typicality, levels = c('typical', 'random', 'atypical'))
test2$reg_rate = factor(test2$reg_rate, levels = c('nc', '-40%', '+40%'))
test2$baseline_av_z = scales::rescale(test2$baseline_av)
test2$pre_reg_av_z = scales::rescale(test2$pre_reg_av)
test2$baseline_av_c = test2$baseline_av - mean(test2$baseline_av)
test2$pre_reg_av_c = test2$pre_reg_av - mean(test2$pre_reg_av)

# lex typ: typical - random - reversed
# reg rate: nc - -40% - +40%
test2$lexical_typicality = test2$lex_typicality
test2$regularisation_rate = ifelse(
  as.character(test2$reg_rate) == 'nc', 'no change',
  as.character(test2$reg_rate)
  )
test2$regularisation_rate = factor(test2$regularisation_rate, levels = c('no change', '-40%', '+40%'))

@@

```{r }
fit1 = brm(resp_post_reg ~ 1 + baseline_av_z * lex_typicality + pre_reg_av_z + reg_rate +
    (1 | participant_id) + 
    (1 | word), 
  data = test2, 
  family = bernoulli, 
  control=list(adapt_delta=0.99, stepsize = 0.01, max_treedepth =15))

@@

```{r }
# the frequentist fit reported in the paper
# watch out for factor levels
test2$verb_baseline_average = test2$baseline_av_c
test2$bot_lexical_typicality = test2$lexical_typicality
test2$participant_prereg_average = test2$pre_reg_av_c
test2$bot_regularisation_rate = test2$regularisation_rate

lme.fit2 = glmer(resp_post_reg ~ 1 + verb_baseline_average * bot_lexical_typicality + participant_prereg_average + bot_regularisation_rate +
    (1 + baseline_av_c | participant_id) + 
    (1  | word), 
  data = test2, 
  family = binomial (link = logit),
  control=glmerControl(optimizer="bobyqa")
)
summary(lme.fit2)$coef

plot(effects::effect('bot_regularisation_rate', lme.fit2), main = '', xlab = 'regularisation shift', ylab = 'regular response in post-test')
plot(effects::effect('verb_baseline_average:bot_lexical_typicality', lme.fit2), multiline = T, lines=list(lty=c(1,2,3)), main = '', xlab = 'verb baseline mean', ylab = 'regular response in post-test')

@@

Here is a simple confint plot using Wald estimates.

```{r }
t1 = broom::tidy(lme.fit2)

# we get some wald confidence intervals

confints = confint(lme.fit2, method = 'Wald') %>% broom::tidy()
confints = confints[-1,]
names(confints) = c('term', '2.5%', '97.5%')
t1 = inner_join(t1, confints) %>% 
  dplyr::select(-p.value,-group)

t1 %>% 
  mutate(
    row_id = 9:1, # watch this
  ) %>% 
  mutate(
    term2 = 
    case_when(
      term == 'verb_baseline_average' ~ 'verb baseline average',
      term == 'bot_lexical_typicalityrandom' ~ 'bot lexical typicality = random',
      term == 'bot_lexical_typicalityatypical' ~ 'bot lexical typicality = atypical',
      term == 'participant_prereg_average' ~ 'participant prereg average',
      term == 'bot_regularisation_rate-40%' ~ 'bot regularisation rate = -40%',
      term == 'bot_regularisation_rate+40%' ~ 'bot regularisation rate = +40%',
      term == 'verb_baseline_average:bot_lexical_typicalityrandom' ~ 'verb baseline average : bot lexical typicality = random',
      term == 'verb_baseline_average:bot_lexical_typicalityatypical' ~ 'verb baseline average : bot lexical typicality = atypical',
      term == '(Intercept)' ~ 'Intercept'
      )
    ) %>% 
  ggplot(aes(x = term2 %>% reorder(row_id), y = estimate)) +
  geom_point() +
  geom_linerange(aes(x = term2, ymin = `2.5%`, ymax = `97.5%`)) +
  geom_hline(aes(yintercept = 0), linetype = 'dashed') +
  xlab('') +
  coord_flip() +
  ggtitle('Estimates and 95% confidence intervals in model for test results')
ggsave('terms_figure.pdf', width = 9, height = 5)

Let's have a few predicted intervals.

@@
